%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Tony}{Prajapati}{ \urlstyle{same}\\
\href{mailto:vqvtony@gmail.com}{vqvtony@gmail.com} | +919011443892 | \href{mailto:tony.prajapati23@pccoepune.org}{tony.prajapati23@pccoepune.org}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{PCCOE Pune}
\descript{Btech in IT }
\location{Third Year | Pune, IN}
\location{SGPA:8.1}
\sectionsep

\subsection{MHT CET}
\location{ 2023 |  Perentile : 98.44}
\sectionsep

\subsection{M J College Jalgaon}
\descript{HSC}
\location{March 2022 | Jalgaon, IN}
Swami Vivekananda \\
Junior College\\

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/gittonyp}{\bf tony} \\
LinkedIn://  \href{ https://www.linkedin.com/in/gittonyp}{\bf tony} \\
Codeforces ://  \href{https://codeforces.com/profile/devtony}{\bf tony} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Coursework}

\subsection{Undergraduate}
Data Structures and Algorithms \\
Database Management Systems (DBMS) \\
Operating Systems \\
Computer Networks \\
Object Oriented Programming (OOP) \\
Software Engineering \\
Artificial Intelligence and Machine Learning \\
Web Technologies \\
Unix/Linux Tools and Scripting \\
Computer Graphics \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
\subsection{Programming}
\location{Over 5000 lines:}
Java \textbullet{} Python \textbullet{} C++ \textbullet{} JavaScript \textbullet{} \LaTeX \\
\location{Over 1000 lines:}
C \textbullet{} HTML \textbullet{} CSS \textbullet{} Shell \textbullet{} PHP \\
\location{Familiar:}
Node.js \textbullet{} Express.js \textbullet{} React.js \textbullet{} MySQL \textbullet{} MongoDB \\
\sectionsep

\subsection{Software Tools \& Platforms}
Git \textbullet{} GitHub \textbullet{} VS Code \textbullet{} Eclipse \textbullet{} NetBeans \\
Linux \textbullet{} Windows \textbullet{} WSL \textbullet{} MiKTeX \\
\sectionsep

\subsection{Systems \& Hardware}
PC Assembly \textbullet{} OS Installation \textbullet{} Troubleshooting \textbullet{} Hardware Upgrades \\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Experience}

\subsection*{Computer Technician | Local Computer Shop}
Assembled and configured custom desktop computers according to client requirements. \\
Installed, managed, and troubleshooted Windows and other operating systems. \\
Performed hardware diagnostics, replacement, and upgrades (RAM, storage, processors, etc.). \\
Resolved software and system issues to ensure reliable performance. \\
Assisted customers with technical support and provided clear, solution-focused guidance. \\



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Projects}

\subsection*{KinderConnect (Full-Stack Web App)}
Developed a childcare and school management platform using React.js, Node.js, Express.js, and MongoDB. \\
Implemented modules for student management, attendance, and communication. \\
Demonstrated strong full-stack web development and database design skills. \\

\subsection*{Railway Reservation System (JavaFX + MySQL)}
Built a desktop-based railway booking system with login, booking, cancellation, and admin panel. \\
Utilized JavaFX for GUI and MySQL as the backend database. \\

\subsection*{Sudoku Solver (JavaFX)}
Created a desktop application to solve Sudoku puzzles using backtracking algorithms. \\
Showcased Java programming, algorithms, and GUI development. \\

\subsection*{Chess Game (C++)}
Designed and implemented a console-based chess game in C++. \\
Applied object-oriented programming principles for piece movement, capturing, and checkmate logic. \\
Utilized data structures (arrays, vectors) for board representation and move validation. \\

\subsection*{UrjaSampda (SIH Prototype)}
Developed a Smart India Hackathon project for energy resource monitoring and management. \\
Designed dashboards and integrated real-time data handling using web technologies. \\

\subsection*{Portfolio Website}
Designed and deployed a personal portfolio website to showcase projects and skills. \\
Built with HTML, CSS, and React.js; deployed on GitHub Pages. \\



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\end{minipage} 
\end{document}  \documentclass[]{article}
