%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Tony}{Prajapati}{ \urlstyle{same}\href{http://devtony.live}{Devtony.live} \\
\href{mailto:vqvtony@gmail.com}{vqvtony@gmail.com} | +919011443892 | \href{mailto:tony.prajapati23@pccoepune.org}{tony.prajapati23@pccoepune.org}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{PCCOE Pune}
\descript{Btech in IT }
\location{First Year | Pune, IN}
\sectionsep

\subsection{MHT CET}
\location{ 2023 |  Perentile : 98.44}
\sectionsep

\subsection{M J College Jalgaon}
\descript{HSC}
\location{March 2022 | Jalgaon, IN}
Swami Vivekananda \\
Junior College\\

\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/gittonyp}{\bf Devtony} \\
LinkedIn://  \href{ https://www.linkedin.com/in/gittonyp}{\bf Devtony} \\
Codeforces ://  \href{https://codeforces.com/profile/devtony}{\bf Devtony} \\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}

\subsection{Undergraduate}
Engineering Math \\
Operating Systems \\
Data Structures and Algo. \\
Functional Programming \\
Computer Graphics + Practicum \\
Linux and Ubuntu \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Over 5000 lines:}
Java \textbullet{}   Shell \textbullet{} Python \textbullet{} Javascript \\ \textbullet{} \LaTeX\ \\ 
\location{Over 1000 lines:}
C \textbullet{} C++ \textbullet{} CSS  \textbullet{} HTML \\
\location{Familiar:}
\textbullet{}
Socket.io  \textbullet{} Android 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

\section*{Projects}

\subsection*{Chess Game in C++}
\begin{itemize}
	\item Developed a console-based chess game using C++.
	\item Implemented the rules of chess, including piece movement, capturing, and check/checkmate conditions.
	\item Utilized object-oriented programming principles to design the game logic.
	\item Demonstrated proficiency in data structures (e.g., arrays, vectors) for board representation.
\end{itemize}

\subsection*{Snake Game in C++}
\begin{itemize}
	\item Created a classic snake game using C++.
	\item Designed the game loop, snake movement, and collision detection.
	\item Utilized data structures (e.g., linked lists or arrays) to manage the snake's body.
	\item Showcased problem-solving skills in handling game mechanics.
\end{itemize}

\subsection*{Function Chatroom Website}
\begin{itemize}
	\item Developed a chatroom website using HTML, CSS, and JavaScript.
	\item Implemented real-time messaging using WebSocket or other communication protocols.
	\item Designed an intuitive user interface for chat interactions.
	\item Demonstrated web development skills and understanding of client-server communication.
\end{itemize}

\subsection*{Portfolio Website}
\begin{itemize}
	\item Designed and built a personal portfolio website.
	\item Showcased your projects, skills, and achievements.
	\item Utilized HTML, CSS, and possibly a front-end framework (e.g., React, Vue.js).
	\item Highlighted your creativity and ability to present information effectively.
\end{itemize}

\end{minipage} 
\end{document}  \documentclass[]{article}
